A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-02 UAM2014/Article/article.tex
la2pdf commit - 2014:05:03	01:11:18	(Sat 3.May)

To obtain the delayed real-time performance we implemented the simulator on a GPU. These devices have a theoretical peak performance that is typically an order of magnitude higher than CPUs in a comparable price range. We experienced that this potential was effectively utilized with a well matured and highly optimized graphics processing API such as OpenGL. Our simulator use this framework for most of the scene processing.

A final post-processing step is performed in OpenCL, which allow general purpose GPU programming. It interoperates well with OpenGL and adds a lot of flexibility to the simulation process. This is valuable as the simulator is still being actively developed and will likely need new features that can not easily be obtained using OpenGL alone.

>>>>

To obtain the delayed real-time performance we implemented the simulator on a GPU. These devices have a theoretical peak performance that is typically an order of magnitude higher than CPUs in a comparable price range. We found this potential to be effectively utilized with the well matured and highly optimized OpenGL graphics processing API. Our simulator use this framework for most of the scene processing.

A final post-processing step is performed in OpenCL, which allow general purpose GPU programming. It interoperates well with OpenGL and adds a lot of flexibility to the simulation process. This is valuable as the simulator is still being actively developed and will likely see new features that can not be easily implemented in OpenGL alone.
